A performance assessment of evolutionary algorithms in a volunteer computing system

### 2016-03-19 PPSN2016/paper.Rnw
Back to 10 pages
Please @mariosky @fergunet @unintendedbear check that out when making corrections

\begin{document}
\SweaveOpts{concordance=TRUE}

@@

Figure \ref{fig:system} describes the general system architecture and
algorithm behavior. Different JavaScript libraries, such as JQuery or {\tt
  Chart.js} have been used to build the user interface elements of the
framework, which should be running in
\url{http://nodio-jmerelo.rhcloud.com}, a free resource hosted in the
OpenShift Platform as a Service.\footnote{It is not guaranteed to be running,
or running the same version, when you read this, however; you can always get
the sources from GitHub and set it up yourself.}
%
\begin{figure}[!t]
\centering
\includegraphics[width=3in]{system.pdf}
\caption{Description of the proposed system. Clients execute a JavaScript EA
  in the browser, which, every 100 generations, sends the best
  individual and receives a random one back from the server.}
\label{fig:system}
\end{figure}

@@

\begin{table}[htbp]
  \caption{Minute-wise correlation for number of participating volunteers. \label{tab:correlation}}
\begin{center}
<<correlations, cache=FALSE,echo=FALSE>>=
ip.correlations$Experiment <- c("base","graph1","reboot","cachereboot")
kable(ip.correlations)
@ %def correlations
\end{center}
\end{table}
%
We can check this impact by looking at the column that refers to
median time in Table \ref{tab:filtered} and its relation to the median
number of PUTs, which reflects the number of evaluations performed by
the clients. The two last rows have a low number of evaluations,
around 650, which is higher than the first two, probably due to the
lower volunteer supply, but better than the middle one; besides, the
amount is remarkably similar. But in the last case, it takes much less
time to find the solution {\em using the same number of
  evaluations}. All variables are difficult to control in this
environment, but it might be due to the fact that parallelism has
increased, there are more volunteers contributing at the same time. In
fact, as it can be seen in the last column, the median number of
contributions per user is {\em much lower} in the last row, which
indicates that {\tt cachereboot} needs less contributions by users to
find the same solution. Besides, the last row shows that {\em all}
users actively contribute to the cache, while in the {\tt reboot}
strategy 30\% of users do not. This might be due to the fact that {\tt
  reboot} only does so when cache size is less than one. With very
fast clients there might be some clients that do not detect that
change and might, in fact continue with their former run, thus not
contributing to the current common cache.

In fact, as can be seen in Table \ref{tab:correlations}, which shows
the correlation between the number of IPs from one minute to the next,
the behavior of all experiments but the last one are similar, with a
very high correlation indicating that the number of volunteers does
not change from one minute to the next. However, there is a sharp drop
for the {\tt cachereboot} experiment, which indicates a bigger
dynamism, with individuals joining and leaving the experiment all the
time. This might be circumstancial, but it also reflects the fact
that the solution is found in less time and that users need less
contributions to find it personally.

>>>>

\begin{document}
%\SweaveOpts{concordance=TRUE}

@@

Figure \ref{fig:system} describes the general system architecture and
algorithm behavior. Different JavaScript libraries, such as JQuery or {\tt
  Chart.js} have been used to build the user interface elements of the
framework, which should be running in
\url{http://nodio-jmerelo.rhcloud.com}, a free resource hosted in the
OpenShift Platform as a Service.
%% \footnote{It is not guaranteed to be running,
%% or running the same version, when you read this, however; you can always get
%% the sources from GitHub and set it up yourself.}
%
\begin{figure}[!t]
\centering
\includegraphics[width=3in]{system.pdf}
\caption{Description of the proposed system. Clients execute a JavaScript EA
  in the browser, which, every 100 generations, sends the best
  individual and receives a random one back from the server.}
\label{fig:system}
\end{figure}

@@

\begin{table}[htbp]
  \caption{Minute-wise correlation for number of participating volunteers. \label{tab:correlation}}
\begin{center}
<<correlations, cache=FALSE,echo=FALSE>>=
ip.correlations$Experiment <- c("base","graph1","reboot","cachereboot")
kable(ip.correlations)
@ %def correlations
\end{center}
\end{table}
%
We can check this impact by looking at the column that refers to
median time in Table \ref{tab:filtered} and its relation to the median
number of PUTs, which reflects the number of evaluations performed by
the clients. The two last rows have a low number of evaluations,
around 650, which is higher than the first two, probably due to the
lower volunteer supply, but better than the middle one; besides, the
amount is remarkably similar. But in the last case, it takes much less
time to find the solution {\em using the same number of
  evaluations}. All variables are difficult to control in this
environment, but it might be due to the fact that parallelism has
increased, there are more volunteers contributing at the same time. In
fact, as it can be seen in the last column, the median number of
contributions per user is {\em much lower} in the last row, which
indicates that {\tt cachereboot} needs less contributions by users to
find the same solution. Besides, the last row shows that {\em all}
users actively contribute to the cache, while in the {\tt reboot}
strategy 30\% of users do not. This might be due to the fact that {\tt
  reboot} only does so when cache size is less than one. With very
fast clients there might be some clients that do not detect that
change and might, in fact, continue with their former run, thus not
contributing to the current common cache.

In fact, Table \ref{tab:correlation}, which shows
the correlation between the number of IPs from one minute to the
next, presents a similar  behavior for all experiments but the last one: a
very high correlation indicating that the number of volunteers changes
slowly. The {\tt cachereboot} experiment correlation indicates a bigger
dynamism, with individuals joining and leaving the experiment all the
time. This might be circumstancial, but it also informs the fact
that the solution is found in less time and that users need less
contributions to find it.
